---
title: "Contributions to the 2016 General Election by Entity Type"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Code

```{r, include=FALSE}
# Load all packages here
library(ggplot2)
library(dplyr)
library(fec16)
library(knitr)
```

```{r, error=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

contributions <- read_all_contributions()

contributions2 <- contributions %>% 
  left_join(candidates, by = "cand_id") %>% 
  filter(cand_pty_affiliation == "DEM" | cand_pty_affiliation == "REP") %>% 
  select(entity_tp, cand_pty_affiliation, transaction_amt) %>% 
  group_by(cand_pty_affiliation, entity_tp) %>% 
  summarize(sum = sum(transaction_amt))

```

## Vizualization

```{r, echo=FALSE}
ggplot(data = contributions2, mapping = aes(x= entity_tp, y = sum,  
      fill = cand_pty_affiliation)) +
  labs(x = "Entity Type", y = "Contribution Amount in Dollars", 
       title = "Contributions to Candidates of the 2016 General Election", 
       fill = "Party") +
  scale_fill_manual(values = c("blue", "red")) +
    geom_bar(stat='identity') +
  facet_wrap(~ cand_pty_affiliation)
```

## A Summary of The Vizualization

This graph shows the contributions to Democratic and Republican candidates in the 2016 general election separated by the type of entity which was contributing. 

One observation from the graph is that the largest contributor to candidates from both parties is organizations (ORG), followed by contributions from candidate committees (CCM), and then finally by contributions not listed as a certain entity type (N/A). The other entity types' contributed proportionately minuscule amounts of money to the campaigns, making organizations and candidate committees the most important and influential contributors. 

Additionally, while Republicans and Democrats received very similar contribution amounts from many of the entities, Republicans received much more from organizations and candidate committees. Republicans had approximately 250 million more dollars in contributions from organizations and approximately 100 million more dollars in contributions from candidate committees than Democrats. 

In regards to the larger amount of contributions from candidate committees, this could be for a variety of reasons including better marketing or fundraising efforts. However, the 250 million dollar difference between the contributions from organizations to Republicans and Democrats is very significant. It is likely that organizations donate more to Republicans because powerful organizations believe that they would benefit better by having Republicans in power as they will be more likely to pass and uphold legislation that would benefit big businesses. For this reason, Republicans receiving more funds from organizations makes sense because they more frequently support large corporations due to their support for policies like lower taxes, less regulation, and smaller government. 
